---
title: "School Diversity Inference Report"
author: "Mohammad Fahim Uddin Alvi, Srabon Ratan, Chunyuan Wang, Keying Rao, Wenyi Wang, Yubin Yao"

output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Load the data set from Github repository

```{r message=FALSE, warning=FALSE}
#load required libraries
library(tidyr)
library(dplyr)
library(ggplot2)
library(gridExtra)

#laod data set 
school_diversity <- read.csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-09-24/school_diversity.csv")

```

## Prepare data


```{r }

#Drop, which populations are less than 100
data <- filter(school_diversity, Total >=500)

#gather different races in one column
data <- gather(school_diversity, "race", "rate", 7:11)

#drop the NA values
data <- filter(data,rate !="NA" )

#remove outliers from their populaton rate 
Q <- quantile(data$rate , probs=c(.25, .75), na.rm = FALSE)
iqr <- IQR(data$rate )
up <-  Q[2]+1.5*iqr # Upper Range  
low<- Q[1]-1.5*iqr # Lower Range

data <- subset(data , data$rate > (Q[1] - 1.5*iqr) & data$rate  < (Q[2]+1.5*iqr))

```


## Distyribution of different Ethinic students in School

```{r warning=FALSE}

data %>% group_by(race) %>% 
  summarise(mean = mean(rate)) %>%
  arrange(desc(mean))  %>% 
  ggplot(aes(reorder(race,-mean),mean, fill= race)) +geom_histogram(stat = "identity")+
  labs(x= "Race",title = "Ethinic distribution in School", y= "Population percentage" )

```


## Adding other races to compare population of White students with all others 

```{r}
data$race[data$race != "White"] <- "Other"


p1 <- ggplot(data,aes(race)) +geom_histogram(stat = "count" )
p2 <- ggplot(data,aes(race,rate)) +geom_boxplot( )
grid.arrange(p1,p2,nrow=1)

```

## Statistical Hypothesis 

Null Hypothesis H0: Population of white students is greater than population of all other races
Alternative Hypothesis Ha: Population of white students is not greater than population of all other races

## checking for assumptions

The assumption for the test is that both groups are sampled from normal distributions with equal variances.

```{r}
#sample 1
qqnorm(data$rate[data$race == "White"])
#sample 2
qqnorm(data$rate[data$race == "Other"])


```


## t-Test

```{r}

t.test(rate ~ race,data, alternative = "greater")

```

## T statistic value 
T statistic value of the test is -142.39

## p value

P value of the test 1

## Decision

As p value is far greater than 0.05 so we are unable to reject the null hypothesis 

## Conclusion

Population of the white students is greater than the population of the student which belong to the other ethnic groups.

